asssignment 1
=====================

Code for loading the data

```{r, echo=TRUE}

activity<-read.csv(file.choose(),header=TRUE)

activity


```

To calculate the total number of steps taken each day,following code was used

```{r,echo=TRUE}

activity$steps

```

Histogram for the above steps taken each day is 

```{r,echo=TRUE}

sumEachDay <- aggregate(steps ~ date, activity, sum)
hist(sumEachDay$steps, col = "grey", breaks = 20,
    xlab = "Number of Steps", xlim = c(0, 25000), ylim = c(0, 20), 
    main = "[Before] Histogram of Total Number of Steps for One Day")

```

Mean and median of toatal number of step taken are:

```{r,echo=TRUE}

mean(sumEachDay$steps, na.rm = TRUE)

median(sumEachDay$steps, na.rm = TRUE)

```

Time plot, where x= 5min interval, y=average steps taken over all the days



For counting NA in the data

```{r,echo=TRUE}

length(which(is.na(activity)==TRUE))

```

Plot

```{r,echo=TRUE}

meanEachInterval <- aggregate(steps ~ interval, activity, mean)
plot(meanEachInterval$interval, meanEachInterval$steps, type = "l", xaxt = "n", 
    xlab = "5-Minute Interval ID (e.g., 730 for interval [07:30, 07:35))", ylab = "Average Number of Steps", 
    main = "Average Number of Steps for Each 5-Minute Interval")
axis(1, c(seq(0, 2400, 200)))

```

The step 

```{r,echo=TRUE}

meanEachInterval[which.max(meanEachInterval$steps),]

```

For replacing NA in the data

```{r,echo=TRUE}

sum(is.na(activity$steps))

newactivity <- activity
for (int in seq(0, 2355, 5)) {
    idx <- which(newactivity$interval == int & is.na(newactivity$steps))
    newactivity[idx, "steps"] <- meanEachInterval[meanEachInterval$interval == int, "steps"]
}

```

Histogram of new data formed

```{r,echo=TRUE}
newSumEachDay <- aggregate(steps ~ date, newactivity, sum)

hist(newSumEachDay$steps, col = "grey", breaks = 20,xlab = "Number of Steps", xlim = c(0, 25000), ylim = c(0, 20),main = "[After] Histogram of Total Number of Steps for One Day")

```




NEW mean and median of the data are:

```{r,echo=TRUE}

mean(newSumEachDay$steps, na.rm = TRUE)

median(newSumEachDay$steps, na.rm = TRUE)

```

As mentioned in the downside, ALL the 8 empty days are all filled in with the same estimates, so the total number of steps in these 8 days are all 10766.19, which equals the mean in sumEachDay. Therefore, the new histogram makes ONLY the mean-value bin higher.
The new mean value is the same because adding the mean values to the original dataset does not change the mean.
The new median value becomes the mean value because 8 mean values are added into the dataset. After sorting, these 8 values will likely dominate in the middle and be picked as the median.. 


